\thetitle

### 2020-11-11 sun_phases/spin_qudit_tomo.tex
simplified expression for exact reconstruction error

The assumption that observables can be estimated up to uncorrelated noise with maximal variance $\epsilon^2$, summarized by Eq.~\eqref{eq:error_assumption}, is reasonable when measurement error is dominated by experimental sources of noise.
However, this assumption breaks down when measurement error is limited by fundamental quantum (shot) noise.
We relax the assumption of Eq.~\eqref{eq:error_assumption} and derive more fundamental error bounds in Appendix \ref{sec:error}.
Therein, we find that if measurement error is dominated by shot noise, then the estimate $\tilde\rho_V$ built from $n$ independent measurements of spin projection along every axis $\v v\in V$ approximates the true state $\rho$ to within a mean squared distance $\epsilon_V^2/n$, i.e.
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2} < \f{\epsilon_V^2}{n},
  \label{eq:bound}
\end{align}
where the {\it error scale} $\epsilon_V^2$ is
\begin{align}
  \epsilon_V^2 \equiv
  \f1d \sum_{\ell>0} \p{2\ell+1} \gamma_\ell^2 \S_{V\ell}^2,
  \label{eq:scale}
\end{align}
and $\gamma_\ell$ is defined using Clebsch-Gordan coefficients:
\begin{align}
  \gamma_\ell
  \equiv \f{\max_\mu\tau_{\ell\mu} - \min_\mu\tau_{\ell\mu}}{2},
  &&
  \tau_{\ell\mu} \equiv \bk{s\mu;\ell,0|s\mu}.
\end{align}
If $d$ even or $\ell$ is odd, then $\gamma_\ell=\max_\mu\tau_{\ell\mu}$.
For comparison with the previous bound in Eq.~\eqref{eq:bound_eps}, the error scale $\epsilon_V^2<\S_V^2/2$, so the previous bound still holds with the replacement $\epsilon^2\to1/2n$.
We note that the bound in Eq.~\eqref{eq:bound} is not tight, as it is acquired by bounding the statistical variance $\epsilon_{\v v\ell}^2$ in the empirical estimate of $\bk{T_{\v v\ell,0}}_\rho$ as $\bbk{\epsilon_{\v v\ell}^2}\le\frac{2\ell+1}{nd}\times\gamma_\ell^2$.
Though the individual bounds for each axis $\v v$ and degree $\ell$ are tight, these bounds cannot be achieved simultaneously.
There is therefore still room for improvement on the bound in Eq.~\eqref{eq:bound}.

As a final comment, we note that Eq.~\eqref{eq:bound} provides a pessimistic upper bound on statistical error, which can be calculated without prior knowledge of the true qudit state $\rho$.
The actual error in the reconstruction $\tilde\rho_V$ of a particular state $\rho$ may be considerably smaller.
To write out this error in full, we identify the normalized right singular vectors $\v x^V_{\ell m}\equiv (x^V_{\ell m,1}, x^V_{\ell m,2}, \cdots)$ and corresponding singular values $M^V_{\ell m}$ of $M_{V\ell}$, and define
\begin{align}
  C_{V\ell i} \equiv \sum_m \abs{\f{x_{\ell m i}}{M^V_{\ell m}}}^2,
  &&
  C_{V\ell} \equiv \sum_i C_{V\ell i} \op{\v v_i}.
\end{align}
We can then compactly express (see Appendix \ref{sec:error})
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \obk{\xi_{V\ell}|\T_{\rho\ell}},
  \label{eq:error}
\end{align}
where
\begin{align}
  \xi_{V\ell} &\equiv M_{V\ell} C_{V\ell} M_{V\ell}^\dag, \\
  \T_{\rho\ell} &\equiv \sum_{m,n}
  \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}} \op{m}{n},
\end{align}
with $\cov_\rho\p{X,Y} \equiv \bk{XY}_\rho - \bk{X}_\rho \bk{Y}_\rho$.
While the error in Eq.~\eqref{eq:error} cannot be known exactly without knowing $\rho$, this error can be estimated by computing the right-hand side of Eq.~\eqref{eq:error} with the replacement $\rho\to\tilde\rho_V$.

@@

Rather than the statistical errors $\epsilon_{i\mu} \equiv \tilde\Pi_{i\mu} - \bk{\Pi_{i\mu}}_\rho$ in the estimates $\tilde\Pi_{i\mu}$ of the projectors $\Pi_{i\mu}$, we now consider the statistical errors $\epsilon_{i\ell} \equiv \tilde T_{i\ell} - \bk{T_{i\ell}}_\rho$ in the estimates $\tilde T_{i\ell}$ of the transition operators $T_{i\ell} \equiv T_{\v v_i\ell,0}$.
We can expand the transition operators $T_{i\ell}$ as a sum over projectors $\Pi_{i\mu}$ as
\begin{align}
  T_{i\ell} = \sum_\mu t_{\ell\mu} \Pi_{i\mu},
  &&
  t_{\ell\mu} \equiv \bk{\mu|T_{\ell,0}|\mu}
  = \sqrt{\f{2\ell+1}{d}} \bk{s\mu;\ell,0|s\mu},
\end{align}
and likewise $\tilde T_{i\ell} = \sum_\mu t_{\ell\mu} \tilde\Pi_{i\mu}$.
The covariance between errors in the transition operator basis is then
\begin{align}
  \bbk{\epsilon_{i\ell} \epsilon_{i'\ell'}}
  = \sum_{\mu,\mu'} t_{\ell\mu} t_{\ell'\mu'}
  \bbk{\epsilon_{i\mu} \epsilon_{i'\mu'}}
  = \delta_{ii'} \times \f1n \sum_{\mu,\mu'} t_{\ell\mu} t_{\ell'\mu'}
  \p{\delta_{\mu\mu'} p_\mu^i - p_\mu^i p_{\mu'}^i}
  = \delta_{ii'} \times \f1n \sp{\bk{T_{i\ell} T_{i\ell'}}_\rho
    - \bk{T_{i\ell}}_\rho \bk{T_{i\ell'}}_\rho}.
\end{align}
In order to establish an upper bound on reconstruction error for an unknown quantum state, we will need an upper bound on the variance $\bbk{\epsilon_{i\ell}^2}$ in particular.
To this end, we observe that
\begin{align}
  \bbk{\epsilon_{i\ell}^2} = \f1n \times \sigma_{p^i}^2\p{t_\ell},
\end{align}
where $t_\ell \equiv \p{t_{\ell,-s},t_{\ell,-s+1},\cdots,t_{\ell s}}$ is a vector of all $t_{\ell\mu}$, and
\begin{align}
  \sigma_p^2\p{X}
  \equiv \sum_\mu p_\mu X_\mu^2 - \p{\sum_\mu p_\mu X_\mu}^2
  = \sum_\mu p_\mu \p{X_\mu - \sum_\nu p_\nu X_\nu}^2
\end{align}
is the variance of $X$ when sampled according to the probability distribution $p$.
The variance $\sigma_p^2\p{X}$ is maximal when $p$ has equal weight on the largest and smallest values of $X$, which implies that
\begin{align}
  \sigma_p^2\p{t_\ell} \le \Gamma_\ell^2,
  &&
  \Gamma_\ell \equiv \f{\max_\mu t_{\ell\mu} - \min_\mu t_{\ell\mu}}{2}.
\end{align}
Altogether, using additionally the fact that $\sigma_p^2\p{t_0}=0$ (because all $t_{0,\mu}=1/\sqrt{d}$) we can bound
\begin{align}
  \bbk{\epsilon_{i\ell}^2}
  \le \f1n \times \Gamma_\ell^2 \times \p{1 - \delta_{\ell,0}}
  = \f{2\ell+1}{nd} \times \gamma_\ell^2
  \times \p{1 - \delta_{\ell,0}},
  \label{eq:variance_bound}
\end{align}
where $\gamma_\ell$ is defined using Clebsch-Gordan coefficients:
\begin{align}
  \gamma_\ell \equiv \f{\max_\mu\tau_{\ell\mu} - \min_\mu\tau_{\ell\mu}}{2},
  &&
  \tau_{\ell\mu} \equiv \bk{s\mu;\ell,0|s\mu}.
\end{align}
Note that the bound in Eq.~\eqref{eq:variance_bound} is tight, as equality is achieved by the mixed state
\begin{align}
  \rho^\star
  \equiv \f12 \p{\Pi_{\v v_i,\mu_{\t{max}}} + \Pi_{\v v_i,\mu_{\t{min}}}},
\end{align}
where $\mu_{\t{max}}$ ($\mu_{\t{min}}$) is any index that maximizes (minimizes) $\tau_{\ell\mu}$.

@@

Equipped with the bound on variances in Eq.~\eqref{eq:variance_bound}, we again consider the block-diagonalized form of the measurement matrix derived in Section \ref{sec:bound}:
\begin{align}
  U M_V = \sum_\ell \op{\ell} \otimes M_{V\ell},
  &&
  M_{V\ell} = \sum_{m,\v v} D^\ell_{m,0} \op{m}{\v v}.
\end{align}
The block diagonal structure of this matrix implies that, rather than an integer index $k\in\set{1,2,\cdots,d^2}$, we can identify the singular values and right singular vectors of $UM_V$ (and equivalently $M_V$) by a block index $\ell\in\set{0,1,\cdots,d-1}$ and a sub-index $m=\set{-\ell,-\ell+1,\cdots,\ell}$.
Making the replacement $k\to\p{\ell,m}$, we can thus repeat the derivations through Eq.~\eqref{eq:bound_eps} of Section \ref{sec:bound} without the assumption of Eq.~\eqref{eq:error_assumption}, finding that
\begin{align}
  \Bbk{\abs{\tilde\rho_{\ell m}^V-\rho_{\ell m}^V}^2}
  = \sum_{i,i'} q_{\ell m i}^V \p{q_{\ell m i'}^V}^*
  \bbk{\epsilon_{i\ell} \epsilon_{i'\ell}}
  = \sum_i \abs{q_{\ell m i}^V}^2
  \bbk{\epsilon_{i\ell}^2}
  < \f{2\ell+1}{nd} \times \gamma_\ell^2
  \times \p{1-\delta_{\ell,0}},
  \label{eq:bound_single}
\end{align}
where $i$ indexes an axis $\v v_i\in V$.
Altogether, we thus find that $n$ measurements of spin projection along every axis $\v v\in V$ allows us to construct an empirical estimate $\tilde\rho_V$ of an unknown state $\rho$ that is accurate to within a mean squared distance
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \sum_{\ell,m} \Bbk{\abs{\tilde\rho_{\ell m}^V-\rho_{\ell m}^V}^2}
  < \f1{nd} \sum_{\ell>0} \p{2\ell+1} \gamma_\ell^2 \S_{V\ell}^2.
  \label{eq:bound_SM}
\end{align}
We note that whereas the bound on $\bbk{\epsilon_{i\ell}^2}$ in Eq.~\eqref{eq:variance_bound} is tight, the bounds in Eq.~\eqref{eq:bound_single} and Eq.~\eqref{eq:bound_SM} are not: the upper bound on $\bbk{\epsilon_{i\ell}^2}$ cannot be achieved simultaneously for all axes $\v v_i$ or degrees $\ell$.
In principle, there is therefore room for improvement on the bound in Eq.~\eqref{eq:bound_SM}.

As a final comment, we note that the statistical error bound in \eqref{eq:bound_SM} is a ``worst-case'' bound that is agnostic to the state $\rho$.
The actual statistical error for any particular state may be considerably smaller, and can be obtained by substituting the exact expression for $\bbk{\epsilon_{i\ell}^2}$:
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \sum_{i,\ell,m} \abs{q^V_{\ell mi}}^2 \bbk{\epsilon_{i\ell}^2}
  = \f1n \sum_{i,\ell} C^V_{\ell i} \sigma_\rho^2\p{T_{i\ell}},
  &&
  C^V_{\ell i} \equiv \sum_m \abs{q_{\ell mi}}^2,
  \label{eq:error_SM_start}
\end{align}
where $\sigma_\rho^2\p{X}\equiv\bk{X^2}_\rho - \bk{X}_\rho^2$ is the variance of $X$.
To simplify this error, we use the fact that all $T_{i\ell}=T_{i\ell}^\dag$ to expand
\begin{align}
  \sigma_\rho^2\p{T_{i\ell}}
  = \sigma_\rho^2\p{\sum_m D^\ell_{m,0}\p{\v v_i} T_{\ell m}}
  = \sum_{m,n} D^\ell_{m,0}\p{\v v_i}^* D^\ell_{n,0}\p{\v v_i}
  \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}},
\end{align}
where
\begin{align}
  \cov_\rho\p{X,Y} \equiv \bk{X Y}_\rho - \bk{X}_\rho \bk{Y}_\rho
\end{align}
is the covariance between $X$ and $Y$.
This expansion allows us to express the error in Eq.~\eqref{eq:error_SM_start} more compactly as
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \p{\xi_{V\ell}|\T_{\rho\ell}},
  \label{eq:error_SM}
\end{align}
where
\begin{align}
  \xi_{V\ell} \equiv M_{V\ell} C_{V\ell} M_{V\ell}^\dag,
  &&
  C_{V\ell}
  \equiv \diag\p{C^V_{\ell,1},C^V_{\ell,2},\cdots,C^V_{\ell,\abs{V}}},
  &&
  \T_{\rho\ell}
  \equiv \sum_{m,n} \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}} \op{m}{n}.
\end{align}
While the error in Eq.~\eqref{eq:error_SM} cannot be known exactly without knowing $\rho$, this error can be estimated by computing the right-hand side of Eq.~\eqref{eq:error_SM} with the replacement $\rho\to\tilde\rho_V$.

>>>>

The assumption that observables can be estimated up to uncorrelated noise with maximal variance $\epsilon^2$, summarized by Eq.~\eqref{eq:error_assumption}, is reasonable when measurement error is dominated by experimental sources of noise.
However, this assumption breaks down when measurement error is limited by fundamental quantum (shot) noise.
We relax the assumption of Eq.~\eqref{eq:error_assumption} and derive more fundamental error bounds in Appendix \ref{sec:error}.
Therein, we find that if measurement error is dominated by shot noise, then the estimate $\tilde\rho_V$ built from $n$ independent measurements of spin projection along every axis $\v v\in V$ approximates the true state $\rho$ to within a mean squared distance $\epsilon_V^2/n$, i.e.
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2} < \f{\epsilon_V^2}{n},
  \label{eq:bound}
\end{align}
where the {\it error scale} $\epsilon_V^2$ is
\begin{align}
  \epsilon_V^2 \equiv
  \f1d \sum_{\ell>0} \p{2\ell+1} \gamma_\ell^2 \S_{V\ell}^2,
  \label{eq:scale}
\end{align}
and $\gamma_\ell$ is defined using Clebsch-Gordan coefficients:
\begin{align}
  \gamma_\ell
  \equiv \f{\max_\mu\tau_{\ell\mu} - \min_\mu\tau_{\ell\mu}}{2},
  &&
  \tau_{\ell\mu} \equiv \bk{s\mu;\ell,0|s\mu}.
\end{align}
If $d$ even or $\ell$ is odd, then $\gamma_\ell=\max_\mu\tau_{\ell\mu}$.
For comparison with the previous bound in Eq.~\eqref{eq:bound_eps}, the error scale $\epsilon_V^2<\S_V^2/2$, so the previous bound still holds with the replacement $\epsilon^2\to1/2n$.
We note that the bound in Eq.~\eqref{eq:bound} is not tight, as it is acquired by bounding the statistical variance $\epsilon_{\v v\ell}^2$ in the empirical estimate of $\bk{T_{\v v\ell,0}}_\rho$ as $\bbk{\epsilon_{\v v\ell}^2}\le\frac{2\ell+1}{nd}\times\gamma_\ell^2$.
Though the individual bounds for each axis $\v v$ and degree $\ell$
are tight, these bounds cannot all be achieved simultaneously.
There is therefore still room for improvement on the bound in Eq.~\eqref{eq:bound}.

As a final comment, we note that Eq.~\eqref{eq:bound} provides a pessimistic upper bound on statistical error, which can be calculated without prior knowledge of the true qudit state $\rho$.
The actual error in the reconstruction $\tilde\rho_V$ of a particular state $\rho$ may be considerably smaller.
To write out this error in full (see Appendix \ref{sec:error} for a derivation), we identify the singular value decomposition
\begin{align}
  M_{V\ell} = U_{V\ell} D_{V\ell} W_{V\ell}^\dag,
\end{align}
and define the $\p{2\ell+1}\times\p{2\ell+1}$ matrices
\begin{align}
  \xi_{V\ell} &\equiv M_{V\ell} \diag\p{W_{V\ell} D_{V\ell}^{-2} W_{V\ell}^\dag} M_{V\ell}^\dag, \\
  \T_{\rho\ell} &\equiv \sum_{m,n}
  \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}} \op{m}{n},
\end{align}
where $\diag\p{X}$ sets all off-diagonal entries of $X$ to zero, and $\cov_\rho\p{X,Y} \equiv \bk{XY}_\rho - \bk{X}_\rho \bk{Y}_\rho$.
We can then compactly express
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \p{\xi_{V\ell}|\T_{\rho\ell}}.
  \label{eq:error}
\end{align}
While the error in Eq.~\eqref{eq:error} cannot be known exactly without knowing $\rho$, this error can be estimated by computing the right-hand side of Eq.~\eqref{eq:error} with the replacement $\rho\to\tilde\rho_V$.

[\red{I think the error in Eq.~\eqref{eq:error} can be maximized with no added cost to computational complexity.
  If so, the second half of this section entire section (as well as Appendix \ref{sec:error}) should be rewritten to replace Eq.~\eqref{eq:bound} by the tighter bound obtained by maximizing Eq.~\eqref{eq:error}.}]

@@

Rather than the statistical errors $\epsilon_{i\mu} \equiv \tilde\Pi_{i\mu} - \bk{\Pi_{i\mu}}_\rho$ in the estimates $\tilde\Pi_{i\mu}$ of the projectors $\Pi_{i\mu}$, we now consider the statistical errors $\epsilon_{i\ell} \equiv \tilde T_{i\ell} - \bk{T_{i\ell}}_\rho$ in the estimates $\tilde T_{i\ell}$ of the transition operators $T_{i\ell} \equiv T_{\v v_i\ell,0}$.
We can expand the transition operators $T_{i\ell}$ as a sum over projectors $\Pi_{i\mu}$ as
\begin{align}
  T_{i\ell} = \sum_\mu t_{\ell\mu} \Pi_{i\mu},
  &&
  t_{\ell\mu} \equiv \bk{\mu|T_{\ell,0}|\mu}
  = \sqrt{\f{2\ell+1}{d}} \bk{s\mu;\ell,0|s\mu},
\end{align}
and likewise $\tilde T_{i\ell} = \sum_\mu t_{\ell\mu} \tilde\Pi_{i\mu}$.
The covariance between errors in the transition operator basis is then
\begin{align}
  \bbk{\epsilon_{i\ell} \epsilon_{i'\ell'}}
  = \sum_{\mu,\mu'} t_{\ell\mu} t_{\ell'\mu'}
  \bbk{\epsilon_{i\mu} \epsilon_{i'\mu'}}
  = \delta_{ii'} \times \f1n \sum_{\mu,\mu'} t_{\ell\mu} t_{\ell'\mu'}
  \p{\delta_{\mu\mu'} p_\mu^i - p_\mu^i p_{\mu'}^i}
  = \delta_{ii'} \times \f1n \cov_\rho\p{T_{i\ell}, T_{i\ell'}},
\end{align}
where $\cov_\rho\p{X,Y} \equiv \bk{XY}_\rho - \bk{X}_\rho \bk{Y}_\rho$.
In order to establish an upper bound on reconstruction error for an unknown quantum state, we will need an upper bound on the variance $\bbk{\epsilon_{i\ell}^2}$ in particular.
To this end, we observe that
\begin{align}
  \bbk{\epsilon_{i\ell}^2} = \f1n \times \sigma_{p^i}^2\p{t_\ell},
\end{align}
where $t_\ell \equiv \p{t_{\ell,-s},t_{\ell,-s+1},\cdots,t_{\ell s}}$ is a vector of all $t_{\ell\mu}$, and
\begin{align}
  \sigma_p^2\p{X}
  \equiv \sum_\mu p_\mu X_\mu^2 - \p{\sum_\mu p_\mu X_\mu}^2
  = \sum_\mu p_\mu \p{X_\mu - \sum_\nu p_\nu X_\nu}^2
\end{align}
is the variance of the entries of $X$ when sampled according to the (classical) probability distribution $p$.
The variance $\sigma_p^2\p{X}$ is maximal when $p$ has equal weight on the largest and smallest values of $X$, which implies that
\begin{align}
  \sigma_p^2\p{t_\ell} \le \Gamma_\ell^2,
  &&
  \Gamma_\ell \equiv \f{\max_\mu t_{\ell\mu} - \min_\mu t_{\ell\mu}}{2}.
\end{align}
Altogether, using additionally the fact that $\sigma_p^2\p{t_0}=0$ (because all $t_{0,\mu}=1/\sqrt{d}$) we can bound
\begin{align}
  \bbk{\epsilon_{i\ell}^2}
  \le \f1n \times \Gamma_\ell^2 \times \p{1 - \delta_{\ell,0}}
  = \f{2\ell+1}{nd} \times \gamma_\ell^2
  \times \p{1 - \delta_{\ell,0}},
  \label{eq:variance_bound}
\end{align}
where $\gamma_\ell$ is defined using Clebsch-Gordan coefficients:
\begin{align}
  \gamma_\ell \equiv \f{\max_\mu\tau_{\ell\mu} - \min_\mu\tau_{\ell\mu}}{2},
  &&
  \tau_{\ell\mu} \equiv \bk{s\mu;\ell,0|s\mu}.
\end{align}
Note that the bound in Eq.~\eqref{eq:variance_bound} is tight, as equality is achieved by the mixed state
\begin{align}
  \rho^\star
  \equiv \f12 \p{\Pi_{\v v_i,\mu_{\t{max}}} + \Pi_{\v v_i,\mu_{\t{min}}}},
\end{align}
where $\mu_{\t{max}}$ ($\mu_{\t{min}}$) is any index that maximizes (minimizes) $\tau_{\ell\mu}$.

@@

Equipped with the bound on variances in Eq.~\eqref{eq:variance_bound}, we again consider the block-diagonalized form of the measurement matrix derived in Section \ref{sec:bound}:
\begin{align}
  U M_V = \sum_\ell \op{\ell} \otimes M_{V\ell},
  &&
  M_{V\ell} = \sum_{m,\v v} D^\ell_{m,0} \op{m}{\v v}.
\end{align}
The block diagonal structure of this matrix implies that, rather than an integer index $k\in\set{1,2,\cdots,d^2}$, we can identify the singular values and right singular vectors of $UM_V$ (and equivalently $M_V$) by a block index $\ell\in\set{0,1,\cdots,d-1}$ and a sub-index $m=\set{-\ell,-\ell+1,\cdots,\ell}$.
Making the replacement $k\to\p{\ell,m}$, we can thus repeat the derivations through Eq.~\eqref{eq:bound_eps} of Section \ref{sec:bound} without the assumption of Eq.~\eqref{eq:error_assumption}, finding that
\begin{align}
  \Bbk{\abs{\tilde\rho_{\ell m}^V-\rho_{\ell m}^V}^2}
  = \sum_{i,i'} q_{\ell m i}^V \p{q_{\ell m i'}^V}^*
  \bbk{\epsilon_{i\ell} \epsilon_{i'\ell}}
  = \sum_i \abs{q_{\ell m i}^V}^2
  \bbk{\epsilon_{i\ell}^2}
  < \f1{\p{M^V_{\ell m}}^2} \times \f{2\ell+1}{nd} \times \gamma_\ell^2
  \times \p{1-\delta_{\ell,0}},
  \label{eq:bound_single}
\end{align}
where $i$ indexes an axis $\v v_i\in V$.
Altogether, we thus find that $n$ measurements of spin projection along every axis $\v v\in V$ allows us to construct an empirical estimate $\tilde\rho_V$ of an unknown state $\rho$ that is accurate to within a mean squared distance
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \sum_{\ell,m} \Bbk{\abs{\tilde\rho_{\ell m}^V-\rho_{\ell m}^V}^2}
  < \f1{nd} \sum_{\ell>0} \p{2\ell+1} \gamma_\ell^2 \S_{V\ell}^2.
  \label{eq:bound_SM}
\end{align}
We note that whereas the bound on $\bbk{\epsilon_{i\ell}^2}$ in Eq.~\eqref{eq:variance_bound} is tight, the bounds in Eq.~\eqref{eq:bound_single} and Eq.~\eqref{eq:bound_SM} are not: the upper bound on $\bbk{\epsilon_{i\ell}^2}$ cannot be achieved simultaneously for all axes $\v v_i$ or degrees $\ell$.
In principle, there is therefore room for improvement on the bound in Eq.~\eqref{eq:bound_SM}.

As a final comment, we note that the statistical error bound in \eqref{eq:bound_SM} is a ``worst-case'' bound that is agnostic to the state $\rho$.
The actual statistical error for any particular state may be considerably smaller, and can be obtained by substituting the exact expression for $\bbk{\epsilon_{i\ell}^2}$:
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \sum_{i,\ell,m} \abs{q^V_{\ell mi}}^2 \bbk{\epsilon_{i\ell}^2}
  = \f1n \sum_{i,\ell} C^V_{\ell i} \cov_\rho\p{T_{i\ell},T_{i\ell}},
\end{align}
where
\begin{align}
  C^V_{\ell i} \equiv \sum_m \abs{q_{\ell mi}}^2
  = \bk{\v v_i| W_{V\ell} D_{V\ell}^{-2} W_{V\ell}^\dag | \v v_i}
\end{align}
can be defined in terms of the singular value decomposition
\begin{align}
  M_{V\ell} = U_{V\ell} D_{V\ell} W_{V\ell}^\dag,
\end{align}
with a unitary matrix $U_{V\ell}$, diagonal matrix $D_{V\ell}$, and isometric matrix $W_{V\ell}$.
Using the fact that all $T_{i\ell}=T_{i\ell}^\dag$, we can expand
\begin{align}
  \cov_\rho\p{T_{i\ell},T_{i\ell}}
  = \cov_\rho\p{T_{i\ell}^\dag,T_{i\ell}}
  = \sum_{m,n} D^\ell_{m,0}\p{\v v_i}^* D^\ell_{n,0}\p{\v v_i}
  \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}},
\end{align}
which implies that
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_{\ell,m,n,i}
  D^\ell_{m,0}\p{\v v_i}^* D^\ell_{n,0}\p{\v v_i} C^V_{\ell i}
  \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}}.
\end{align}
Altogether, we can define the $\p{2\ell+1}\times\p{2\ell+1}$ matrices
\begin{align}
  \xi_{V\ell} \equiv M_{V\ell}
  \diag\p{W_{V\ell} D_{V\ell}^{-2} W_{V\ell}^\dag} M_{V\ell}^\dag
  &&
  \T_{\rho\ell} \equiv
  \sum_{m,n} \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}} \op{m}{n},
\end{align}
where $\diag\p{X}$ sets all off-diagonal entries of $X$ to zero, and compactly express
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \p{\xi_{V\ell}|\T_{\rho\ell}}.
  \label{eq:error_SM}
\end{align}
While the error in Eq.~\eqref{eq:error_SM} cannot be known exactly without knowing $\rho$, this error can be estimated by computing the right-hand side of Eq.~\eqref{eq:error_SM} with the replacement $\rho\to\tilde\rho_V$.
